\documentclass{letter}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{eurosym}



\usepackage[a4paper,left=4.5cm,right=4.5cm,top=2.5cm,bottom=2.5cm]{geometry}



\begin{document}
\begin{letter}{
	U.S. Embassy Paris \\ 
	4 Avenue Gabriel \\
	75382 Paris Cedex 08 \\
	France
}

\signature{Aghiles DJOUDI}
\address{
	Aghiles DJOUDI \\ 
	\textbf{Tel:} +33 7 80 73 35 11 \\ 
	\textbf{Email:} aghilesdjoudi@gmail.com \\ 
	\textbf{Address:} 11 rue des sorrières, 92160,Antony
}

\opening{Dear Consul,}

My name is Aghiles DJOUDI,
	I am an Algerian citizen with a French permanent residence.
I was born on August 14th, 1993 in SIDI M'HAMED (Algiers).

After my Master graduation at Sorbonne university in September 2017.
I was hired as a research engineer at Sorbonne university laboratory (lip6) in 2018.
Now I am a PhD student at Paris-Est University,
	I work on a smart city project.

My paper "Social privacy score through vulnerability contagion process" that I wrote with Pr. Guy Pujolle at Sorbonne university,
	was accepted in MobiSecServ conference.
The conference will be organized on \textbf{March 2nd and 3rd, 2019 in the "Grand Beach Hotel", 4835 Collins Ave, Miami Beach, FL 33140}.
The conference program and my name are clearly mentioned in the conference web page "\textbf{mobisecserv.org}" for further information.

To be present at this important appointment,
	all travel funds (airline tickets, the hotel, the visa request and the conference registration) will be covered by Sorbonne University.
The travel Administrator from Sorbonne University is \textbf{Mr. KAMDEM Eugène,
	Tel: +33 1 44 27 87 36,
	Email: Eugene.Kamdem@lip6.fr}.
We are patiently waiting for the answer to our visa application to validate the hotel and the airline reservations payment.

I plane to travel to Miami International Airport on March 1st and return on March 6th 2019 by the same airport.
I will stay in a hotel which is close to the conference location, namely \textbf{"Casablanca on the Ocean East Tower Hotel", 6345 Collins Ave, Miami Beach, FL 33141,
Tel : +1 305-868-0010}

Thank you for your time and consideration.

\closing{Yours Faithfully,}

%\ps P.S. You can find the full text of GFDL license at
%\url{http://www.gnu.org/copyleft/fdl.html}.
%\encl{Copyright permission form}
%\ps{:Post Scriptum}
\end{letter}
\end{document}
