\begin{abstract}

%Cause1
The exponential grow of IoT application in different industries raises many questions in wireless network field.
%Cause2
Heterogeneous networks of IoT applications strongly depend on the ability on IoT devices to adapt their data transmission parameters to the application requirement running at each time.
% Problem
One of the most important problem of IoT network is that IoT devices are limited in terms of energy consumption and computation capability.
% Motivation
Our work is motivated by the idea of matching each transmission configuration with a reward and cost values to satisfy Iot application requirements.
% Goal
Our goal is to make IoT devices able to select the optimal configuration to transmit their data to the gateway with the QoS required by the application running on the device.
% Challenges
Determining the best configuration among 6356 possibilities is difficult due to the lack of tools that could take both applications requirements and external environment in consideration to select the best transmission parameters.
% Approach1
To address this problem,
we use a genetic algorithm in a fog computing to select the transmission parameters needed by the application.
Genetic algorithms are used in selection and ranking problems to model the natural selection of chromosomes in human generation.
In our case, each configuration represents a chromosome that need to be selected to match better the QoS criteria.
% Approach2
Particularly,
	we analyze the impact of selecting one configuration in 3 kinds of applications: text, voice and image transmission by modeling a new adaptive configuration selection process.
% Validation
We validate our approach by using both simulation and real environment testbed.

% % Results1
% Simulation results show that over-trusting vulnerable users speeds the vulnerability diffusion process through the network.
% % Results2
% Furthermore,
% 	vulnerable users with high reputation level lead to a high convergence level of infection,
% 	this means that the vulnerability contagion process infects the biggest number of users when vulnerable users get a high level of trust from their interlocutors.

\end{abstract}


