\documentclass[11pt, a4paper]{.awesome-cv}

\fontdir[fonts/]

\newcommand*{\sectiondir}{cv/}

\headersocialsep[\quad\textbar\quad]

\colorlet   {awesome}  {awesome-red}
\definecolor{awesome}  {HTML}       {4440bF}
\definecolor{darktext} {HTML}       {414141}
\definecolor{text}     {HTML}       {414141}
\definecolor{graytext} {HTML}       {414141}
\definecolor{lighttext}{HTML}       {414141}

\name     {DJOUDI                                         }{Aghiles}
\address  {xx, rue des sorrières, 92160, Antony           }        
\mobile   {0780.73.35.11                                  }        
\email    {aghilesdjoudi@gmail.com                        }        
%\homepage{www.posquit0.com                               }        
\github   {Aghiles8                                       }        
\linkedin {aghiles-djoudi-b4b9a3113                       }        
\position {Network Security Engineer}        

\letterdate                   {\today}
\lettertitle                  {Thesis Application}
\letteropening                {Dear Hiring Team,}
\letterclosing                {Sincerely,}
\letterenclosure[Attached]{Curriculum Vitae}

\makecvfooter
	{\today}
	{Aghiles DJOUDI~~~·~~~Cover Letter}
	{Thesis Application}

\def\cloture{
	\color{black}{
		Thank you for your time and consideration.
	}
}

\def\reference#1{\quote{\textbf{Application reference:} {#1}}}

%%%%

\def\entreprise{This subject }

\reference{PhD Position on Network visibility with Machine Learning (seen in rsd forum)}

\recipient{Organismes d'accueil}{
	MATHEMATICAL AND ALGORITHMIC SCIENCES LAB \\
	FRANCE RESEARCH CENTER, HUAWEI TECHNOLOGIES CO., LTD.
}

\begin{document}

\makecvheader
\makelettertitle

\begin{cvletter}
	\cvparagraph{About Me}
	\color{black}{
		Holder of a research master in network security engineering at the University of Pierre and Marie Curie (UPMC) in Paris.
		I was ranked fifth among 111 students in M2.
		I want to continue my studies and prepare a thesis in the field of machine learning applied on networking.
		I'm currently working as a research engineer with the PHARE team at Lip6 laboratory in Sorbonne University.
		I contribute on writing a research paper with one of the PhD students of the laboratory.
		I consider myself to be very ambitious,
			this drives me to give the best of myself to successfully meet daily challenges.
	}

	\cvparagraph{Why this subject ?}
	\color{black}{
		I am interested in this subject because it perfectly matches my past experiences,
			my study path and my future ambitions.
%		\entreprise will allow me to gain a solid foundation in the implementation of new paradigms to reduce latency.
		Succeeding \ this thesis will validate my ability to find new solutions in current network challenges and particularly in gaining visibility into encrypted traffic.
		The topic you are proposing will predict (with minimum false and negative errors) which kind of encrypted traffic we are facing.
		Indeed,
			this initiative will allow to better manage traffic with the respect of users privacy.
		As a consequence,
			finding a trade-off between identifying new traffics and identifying behavioral changes in old traffic becomes a challenge that deserves a lot of attention.
	}

	\cvparagraph{Why Me ?}
	\color{black}{
		The computer network is at the heart of my work, academic projects and my professional experiences.
		I have skills in modeling as in programming and writing,
		I will be able to model and implement my solutions and write research papers.
		Furthermore,
			with the knowledge acquired in machine learning during my academic projects and professional experiences.
			as well as my internship at the Higher Institute of Automotive and Transport (ISAT) on the quality of service analysis of V2P communications,
			and my recent experience in doing research as a research engineer this year at Sorbonne University,
		I have the deep conviction of the success of my thesis project within your company.
	}
	
\end{cvletter}

\cloture

\makeletterclosing

\end{document}



