\begin{abstract}

% Cause of the problem 1
The exponential grow of IoT application in both industry and academic research raises many questions in wireless sensor network.
% Cause of the problem 2
Heterogeneous networks of IoT devices strongly depend on the ability of IoT devices to adapt their data transmission parameters to the application requirement running at each time.
% The problem 
One of the most important problem of the emerging IoT networks is that IoT devices are limited in terms of energy consumption and computation capability.
% Motivation to solve this problem
Our work is motivated by the idea of matching each transmission configuration with a reward and cost values to satisfy applications requirements.
% Goal
Our goal is to make IoT devices able to select the optimal transmission configuration and send their data to the gateway with the QoS required by the application running on the device.
% Challenges
Determining the best configuration among 6720 transmission configurations is difficult,
	this is mainly due to the lack of tools that could take both applications requirements and external environment in consideration to select the best transmission parameters.
% Approach 1
To address this problem,
	we use a genetic algorithm in an edge computing to select the transmission parameters needed by the application.
Genetic algorithms are used in selection and ranking problems to model the natural selection of chromosomes in human generation.
In our case, 
	each configuration represents a chromosome that needs to be selected to match better the QoS criteria.
% Approach 2
Particularly,
	we analyze the impact of selecting one configuration in 3 kinds of applications: text, voice and image transmission by modeling a new adaptive configuration selection process.
% Validation
We validate our approach by using both simulation and a real environment testbed.

% % Results1
% Simulation results show that over-trusting vulnerable users speeds the vulnerability diffusion process through the network.
% % Results2
% Furthermore,
% 	vulnerable users with high reputation level lead to a high convergence level of infection,
% 	this means that the vulnerability contagion process infects the biggest number of users when vulnerable users get a high level of trust from their interlocutors.

\end{abstract}


